A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-07 paper/main.tex
Disable pieces that are out-of-scope for the paper IMHO

\todo[inline]{Ausführliche Beschreibung bzgl. Sentences in Tabelle; ich finde es in der Form hier so ok/besser.}
For this publication, we annotated the exact onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e. the audio-only variant of the movie)\citep{ForrestGumpDVD}(see Table \ref{tab:overview} for an overview of the annotation's content).
fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
Additional fMRI data of this dataset include the perception of musical genres \citep{hanke2015musical}, and retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.

\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.}
The current annotation facilitates modelling of hemodynamic brain responses
correlating with speech-related events in the two stimuli.
It extends already available annotations of portrayed emotions \citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional confound measures describing key properties of major building blocks of the stimulus.

>>>>

For this publication, we annotated the exact onsets and offsets, and content of
sentences, single words, and phonemes spoken in the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e. an
audio-only variant of the movie)\citep{ForrestGumpDVD}.
% immediate reference not needed in the intro
%(see Table \ref{tab:overview} for an overview of the annotation's content).

fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% the following seems unrelated to the scope of the paper
%Additional fMRI data of this dataset include the perception of musical genres
%\citep{hanke2015musical}, and retinotopic mappings and localization of higher
%visual areas of the same participants \citep{sengupta2016extension}.
The annotation presented here facilitates modelling of hemodynamic brain responses
correlated with speech-related events in the two stimuli.
It extends already available annotations of portrayed emotions
\citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy},
as well as cuts and locations depicted in the movie
\citep{haeusler2016annotation}.  All annotations can be used in any study
focusing on other aspects of real-life cognition by serving as additional
confound measures describing key properties of major building blocks of the
stimulus.

\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.}
